---
output: rmarkdown::github_document
---

`mywx` : Tools to Query the 'MetMalaysia' Web Service 'API'

The following functions are implemented:

- `mywx_districts`:	Retrieve valid geopolitical entities (location)
- `mywx_forecast`:	Retrieve forecast data for a location
- `mywx_states`:	Retrieve valid geopolitical entities (location)
- `mywx_touristdests`:	Retrieve valid geopolitical entities (location)
- `mywx_towns`:	Retrieve valid geopolitical entities (location)

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/mywx")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

### Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(mywx)
library(tidyverse)

# current verison
packageVersion("mywx")

mywx_districts()

mywx_states()

mywx_towns()

mywx_touristdests()

glimpse(mywx_forecast("LOCATION:237", "2017-08-13", "2017-08-13"))

vals <- mywx_forecast("LOCATION:237", "2017-08-01", "2017-08-13")

glimpse(vals)

dplyr::filter(vals, datatype %in% c("FMINT", "FMAXT")) %>% 
  mutate(value = as.numeric(value)) %>% 
  ggplot(aes(date, value, color = datatype)) +
  geom_line()
```

### Test Results

```{r message=FALSE, warning=FALSE, error=FALSE}
library(mywx)
library(testthat)

date()

test_dir("tests/")
```

